Distributed Version Control Systems

### 2010-06-07 laarsample.tex
Agregados keywords. Modificada la parte de bibliografía

%TCIMACRO{\TeXButton{keywords}{\keywords}}
%BeginExpansion
\keywords%
%EndExpansion
Por favor, incluya hasta cinco palabras clave que identifiquen en forma concreta su trabajo.
\endkeywords

@@

\bibitem{linusgit}
Linus Torvalds
\newblock \emph{Google Talk presentation on Git}

\bibitem{perforceclientspec}
Perforce documentation on ``Editing Client Specs''

\newblock \emph{
http://www.perforce.com/perforce/doc.current/manuals/p4web
/help/editclient.html
}

\bibitem{svnmerging}
Git-SVN Crash Test Course
\newblock \emph{http://git.or.cz/course/svn.html\#merge}

\bibitem{dvcsperfcomparison}
DVCS Performance Comparison
\newblock \emph{http://ldn.linuxfoundation.org/article/dvcs-round-one-system-rule-them-all-part-3}

\bibitem{interfaces}
Kernel.org wiki Git Interfaces Comparison
\newblock \emph{https://git.wiki.kernel.org/index.php/Interfaces,\_frontends\_and\_tools\#Graphical\_Interfaces}

>>>>

%TCIMACRO{\TeXButton{keywords}{\keywords}}
%BeginExpansion
\keywords%
GIT, SVN, DVCS, MERCURIAL
\endkeywords

@@

\bibitem{linusgit}
Linus Torvalds \emph{Google Talk presentation on Git}

\bibitem{perforceclientspec}
Perforce documentation on ``Editing Client Specs''
\emph{
http://www.perforce.com/perforce/doc.current/
manuals/p4web/help/editclient.html
}

\bibitem{svnmerging}
Git-SVN Crash Test Course
\emph{http://git.or.cz/course/svn.html\#merge}

\bibitem{dvcsperfcomparison}
DVCS Performance Comparison
\emph{http://ldn.linuxfoundation.org/article/
dvcs-round-one-system-rule-them-all-part-3}

\bibitem{interfaces}
Kernel.org wiki Git Interfaces Comparison
\emph{https://git.wiki.kernel.org/index.php/
Interfaces,\_frontends\_and\_tools\#Graphical\_Interfaces}
